Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
start repro sub-section

>>>>

 Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
 A key element is professional software management and engineering, and the central technology solution is version control. 
 Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \citep{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.
